### 2015-05-27 technical-background.tex
barco ip
FPGA theory

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{FPGA}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Driving from the OS: basically, they will need to share some memory.
That memory can be directly mapped and accessed from the user-space using \texttt{/dev/mem}, or can use a direct memory access module (DMA).
From the operating system, we build a bunch of scatterlist in the kernel-space memory, then map those pages to memory descriptor that have a physical address on the DMA.
They can be mapped three different ways: \texttt{DMA\_BIDIRECTIONAL}, \texttt{DMA\_TO\_DEVICE} or \texttt{DMA\_FROM\_DEVICE}.
When the CPU write something in those descriptors and synchronize them with the DMA, it does not have to care about them anymore, the DMA in now in charge to send them to the device where registers are ready to read the incomming data.
The same goes from the device to the CPU: when the device wants to communicate data to the OS, it writes it on the DMA that will transfer them to the CPU, triggering a flag on the way to notify it.

+ talk about the slave/master and the two data paths: data and control.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{FPGA}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
The aim of this work is to study the impact of offloading cryptographic operations in hardware.
In order to reach that goal, an FPGA will be used.

A Field-Prgrammable Gate Array (FPGA) is an integrated circuit that can be programmed after the manufacturing, using a semiconductor intellectual property core (IP core).
In this work, we will use some of Barco Silex's crypto IP cores.

In order for the operating system to comunicate with the device, they will need to share some memory.
That memory can be directly mapped and accessed from the user-space using \texttt{/dev/mem}, or can use a direct memory access module (DMA).
From the operating system, we build a bunch of scatterlist in the kernel-space memory, then map those pages to memory descriptor that have a physical address on the DMA.
They can be mapped three different ways: \texttt{DMA\_BIDIRECTIONAL}, \texttt{DMA\_TO\_DEVICE} or \texttt{DMA\_FROM\_DEVICE}.
When the CPU write something in those descriptors and synchronize them with the DMA, it does not have to care about them anymore, the DMA in now in charge to send them to the device where registers are ready to read the incomming data.
The same goes from the device to the CPU: when the device wants to communicate data to the OS, it writes it on the DMA that will transfer them to the CPU, triggering a flag on the way to notify it.

+ talk about the slave/master and the two data paths: data and control.
figure~\ref{fig:barco-ba411e-ipcore} shows a schematic view of a Barco Silex' crypto IP core
\begin{figure}
\includegraphics[width=\linewidth]{barco-ba411e-ipcore}
\caption{Barco Silex' AES IP Core}{There are two channels to comunicate with the IP core: the data and control paths~\cite{barco-ba411e}.}
\label{fig:barco-ba411e-ipcore}
\end{figure}

There are two types of interface with such a device: master or slave.
The figure~\ref{fig:barco-ba411e-ipcore}  represent one of Barco Silex' crypto IP cores that proposes two interfaces: one of each type.
\begin{itemize}
	\item The data path is a master. That is the operating system will not have a direct access to the memory registers of the hardware devide. Instead, they will communicate via a DMA bus: one peer places data on the DMA and notifies the other that he can fetch it.
	\item The control (ctrl) path is a slave. The operatin system can directly read and write on this part of the device memory.
\end{itemize}

A master interface has the advantage to offload a part of the memory management to the device, but there is a space overhead to connect the DMA as well as an extra delay to process its data.
A slave interface is usually used for sporadic data, avoiding the overhead of a DMA.
As an example, the data path of Barco Silex' symmetric cryptography IP core is a master, as there is a lot of data to process, whilst the same data path of their asymmetric cryptography IP core is a slave, for the operands are larger and the computation takes more time.
